---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AAGIQuartoExtra

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/jafernandez01/AAGIQuartoExtra/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jafernandez01/AAGIQuartoExtra/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of AAGIQuartoExtra is to make use of AAGI Quarto templates a bit easier.
It provides convenience functions to create AAGI Quarto projects and update current projects with the most recent templates.

## Installation

You can install the development version of AAGIQuartoExtra from [GitHub](https://github.com/) with:
      
``` r
# install.packages("devtools")
devtools::install_github("jafernandez01/AAGIQuartoExtra")
```

## Example

This is a basic example which shows you how to create a new AAGI project:

```{r example}
library(AAGIQuartoExtra)
## basic example code
```
