---
# ======================= USER INPUT SECTION ============================
# Modify the following fields as needed

# General Information
report-series: "Analytics for the Australian Grains Industry - University of Adelaide (AAGI-UA)"  # Report series name

# Document Title and Subtitle
title: "Informative Title for Report"        # Main title of the report
subtitle: "Report for \\<Project Number\\>"  # Subtitle, modify as required

# Author Information
author:                                      # List of authors
  - "**Your Name**"   # Surround with ** to bold
  - "Name 2"
  - "Name 3"
email: "your.email@adelaide.edu.au"          # Contact email for the primary author(s)

# Additional Display Options
lot: false                                   # List of Tables (true/false)
lof: true                                    # List of Figures (true/false)
pagebreak-before-h1: true                    # Pagebreak before level 1 headings (true/false)
partner-logo: #"_extensions/aagi-report/assets/AAGI_logo.png"  # Path to the partner logo (PNG version)
bibliography: references.bib                 # Path to bibliography file

# ===================== END OF USER INPUT SECTION ========================

# ====================== INTERNAL SETTINGS ===============================
# Do not modify the following fields; required for consistent formatting

# Automatic date generation
date: today                                  # Auto-generate date
date-format: long                            # Full date format (e.g., "October 2, 2024")

# Formatting Output
format:                                      # Output formats supported by the template
  aagi-report-pdf: default                          # PDF formatting using custom style
  aagi-report-docx: default                         # DOCX formatting using custom style
  aagi-report-html: default                         # HTML formatting using custom style
---

# Executive Summary {.unnumbered}

Executive summary goes here. Summarise the work that was provided by AAGI and the main results. (Try to limit this to a single page.)

# Introduction

The report body text goes here. The section titles are provided as a guide and for consistency across reports [@ggplot2], but feel free to modify them if they are not relevant or if using a different set of titles enhances the readability of your report. Use theme colours for emphasis if you like (\textcolor{AAGIblue}{AAGI blue: \#00808b}, \textcolor{AAGIgreen}{AAGI green: \#b6d438}, \textcolor{AAGIblack}{AAGI black: \#414042}).

In this Introduction section, outline the goals of the research project and any necessary background to provide contexts and rationale for the research/work.

## This is a subsection

Use subsections (and subsubsections) as much as you like to help structure your content.

### This is a subsubsection

### Structure

::: {.panel-tabset}
```{r}
str(data.frame(pressure))
```

### Data Table

```{r}
print(pressure)
```

### Summary table

```{r}
summary(pressure)
```
:::

# Trial design

Include the trial layout, type, and the experimental design, such as treatments, number of replicates, blocking, etc. Include graphics and pictures where useful.

Make sure to include notes about any specific considerations that must be kept in mind for the type of trial (e.g., small plots, glasshouse experiments, genetics, breeding trials, OFE projects, bioinformatics projects, and so on).

# Exploratory data analysis

You can use a dedicated section here for the preliminary data exploration and dataset visualisation. This can be useful to aid in the interpretation of the data and graphs generated throughout the work, as well as for providing a rationale for the statistical methodologies used.

# Methods

Use this section to include a detailed description of the procedures and methodologies used for the analysis. Include versions/commits on developed pipelines, code scripts, and input/output details as relevant.

Detail also the approach taken for the data analysis work here (or in a separate section [@Monteith1977]).

# Results and discussion

Include all of the results of the analytical work, and discuss the findings and their implications with respect to the research question.

::: landscape-section
Example R code for generating @fig-example1 in a landscape layout:

```{r, echo=FALSE}
#| fig.cap: "Example plot"
#| label: fig-example1
plot(pressure)
```
:::

# Datasets and metadata

(Optional) Where useful, include descriptions of the datasets relevant to this research, including links and DOIs to enable findability of these datasets. (Often for GRDC projects these will have associated metadata entries in the GRDC Data Catalogue, which can be linked where appropriate.)

Where you have publicly available code on GitHub associated with the analytics (e.g., pipelines), you can include git commit numbers and tags. Including md5/sha256 checksums for input data and outputs is also useful for research reproducibility.

# Trial location maps

(Optional) Include if relevant to the project.

# References

Include a bibliography of cited works and literature at the end.

::: {#refs}
:::

\aagiappendix

# This is an appendix

Include Appendices at the end of the report as necessary, to contain any additional supporting information of interest.

```{r, echo=TRUE, results='asis', eval=FALSE}
# Here a sample R code chunk demonstrating how to include R code in the doc.
# The following code simulates data and performs a linear regression.

# Load necessary libraries
library(ggplot2)

# Simulate some data
set.seed(123)
n <- 100
x <- rnorm(n)
y <- 2 * x + rnorm(n)

# Create a data frame
data <- data.frame(x = x, y = y)

# Fit a linear model
model <- lm(y ~ x, data = data)

# Summary of the model
summary(model)

# Plot the data and the fitted regression line
ggplot(data, aes(x, y)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  labs(title = "Scatter Plot with Regression Line",
       x = "Predictor (x)",
       y = "Response (y)")
```

# This is another appendix

Include as many appendices as you like.
